Threat detection in online discussions

### 2016-04-02 submission.tex
Finished the significance and held-out portions

\paragraph{Tuning}
When tuning each model, we aim to maximize the F-score. For the MaxEnt and SVM classifiers we tune the regularization parameter (C), where a smaller value corresponds to stronger regularization. When tuning these classifiers, we start with C-values from 1 to 150 in 10-value increments, select the best performing C-value and repeat the process with decreasing increments, with the range of C-values centered on the best performing C-value thus far. After 6 iterations, we terminate the tuning, and select the best performing C-value. When tuning the Random Forest classifier, we perform a grid search over the maximum number of features used when splitting a node in the tree %% (sqrt($n$), log($n$) or $n$, where $n$ is the number of features in the model)
, and the number of trees %% (10, 100 or 1000, depending on the size of the feature set)
. In the following experiments, we perform tuning on all feature sets.

@@

Next, we include feature types based on the other information sources listed above, i.e., POS, dependencies, WordNet synsets, and Brown clusters. All these features are instantiated both with the \emph{bag-of} feature template on their own, and in combination with the bag-of-words features. As seen in Table~\ref{tab:bagOfFeatures}, none of the feature types alone yield higher F-scores than bag-of-words. On the other hand, when combined with BoW, all feature types (except the lexicalized POS-tags) perform better than BoW alone. However, none of them outperform BoW and BoL combined (F=$0.6278$, cf. Table~\ref{tab:ngrams}), or the combination of Bow+BoL with $n$-grams (F=$0.6656$).

@@

    \end{tabular}
  \end{center}
  \caption{Backoff from different combinations of $n$-grams. The models also
    contain bag-of-words and the other \emph{bag-of} features. Each backoff combination is the one that achieved the best result.}
  \label{tab:ngrambackoff}
  \end{smaller}
\end{table}

Next, the $n$-grams and \emph{bag-of} features are combined with generalized versions of $n$-gram features using the `backoff' strategy described in the previous section. In Table~\ref{tab:ngrambackoff} we see that the lemma backoff consistently outperform the other feature types, but that even lemma backoff does not improve upon the results without backoff features. We test all possible backoff combinations.
% fixme: forklar mer eksplisitt hvilke trekk som inngår i modellene i tabell 5, jeg klarte ikke gjøre rede for det selv.

@@

Lastly, we will test the addition of dependency triples to our models. We add
dependency triples consisting of word forms, both alone, and in conjunction
with feature backoffs. We test both head-backoff and modifier-backoff, and we report the variant that achieved the best results. As seen in Table
\ref{tab:depbackoff}, the inclusion of word form dependency triples improved
upon the simplest model, with an F-score of $0.6240$, compared to $0.6123$ for
bag-of-words alone. Dependency triples did not, however, improve upon the
results achieved by our previous best performer with an F-score of $0.6656$. %, as the best model with dependency triples got an F-score of $0.6586$ compared to our best result of $0.6656$.
The addition of backoff also did not improve the results above the previous best performer.
%% Neither did the addition of backoff improve upon this. Adding POS backoff
%% to the `BoW+dep' configuration resulted in a slightly increased F-score of
%% $0.6298$. However, adding backoff to the `All' feature set only resulted in poorer F-scores, with the best feature backoff (also POS) resulting in an F-score of $0.6547$.

For the development data then, our best performer remains the feature set comprising bag-of-word forms, bag-of-lemmas, and word form bigrams and trigrams; with an F-score of $0.6656$. We will refer to this model as `lexical $n$-grams'. % fixme: burde kanskje ha introdusert denne termen tidligere?

@@

%% Before we perform our held-out testing, we will examine what types of errors we have in our model, when tested on the development set. 
The lexical $n$-gram feature set achieved a precision (P) of $0.7709$ and a recall (R) of $0.5857$. The performance of the same feature set improved slightly when using the SVM classifier (F=$0.6667$, P=$0.7629$, R=$0.5920$).
Compared with our initial BoW system, which had P=$0.6777$ and R=$0.5585$, we see that the majority of the improvement comes from the increase in precision. Both increases are statistically significant, with p-values of $1.3\mathrm{e}{-11}$ and $8.6\mathrm{e}{-11}$ for the lexical $n$-gram system using MaxEnt and SVM, respectively, when comparing with BoW, using the Wilcoxon significance test. When reviewing a random sub-sample of the false positives and false negatives, we see that the noisy data has caused some problems for the pre-processor. % fixme: kanskje forklare mer hva det siktes til her?
Another source of errors, specifically for precision, are comments which use multiple typically threatening words in a non-threatening context.

@@

We performed our final testing on the held-out test set using the basic BoW model and the lexical $n$-gram model. The held-out test set consists of 5,685 sentences, 281 of which are threats, and we train on the entire development set. As seen in Table~\ref{tab:heldout}, the $n$-gram model outperforms the BoW model by a good margin, with F-scores of $0.6860$ and $0.6562$ respectively. However, the difference in F-scores between the two feature sets is not as large as on the development data, and they are in fact not statistically significant, with p-values of $0.14$ and $0.16$, when comparing the MaxEnt and SVM lexical n-gram models, respectivley, to BoW, using Wilcoxon. At the same time, we see that all the models actually achieves higher scores on the held-out data than the development data, and this effect is particularly strong for the BoW model (with the F-score going up from $0.6123$ to $0.6562$). % fixme: noen teori om hvorfor vi ser denne effekten?
% fixedfixme: si noe som størrelsen på held-out dataene.

>>>>

\paragraph{Tuning}
When tuning each model, we aim to maximize the F-score. For the MaxEnt and SVM classifiers we tune the regularization parameter (C), where a smaller value corresponds to stronger regularization. When tuning these classifiers, we start with C-values from 1 to 150 in 10-value increments, select the best performing C-value and repeat the process with decreasing increments, with the range of C-values centered on the best performing C-value thus far. After 6 iterations, we terminate the tuning, and select the best performing C-value. When tuning the Random Forest classifier, we perform a grid search over the number of trees, and the maximum number of features used when splitting a node in the tree. %% (sqrt($n$), log($n$) or $n$, where $n$ is the number of features in the model)
%% , and the number of trees 
%% (10, 100 or 1000, depending on the size of the feature set)
In the following experiments, we perform tuning on all feature sets.

@@

Next, we include feature types based on the other information sources listed above, i.e., POS, dependencies, WordNet synsets, and Brown clusters. All these features are instantiated both with the \emph{bag-of} feature template on their own, and in combination with the bag-of-words features. As seen in Table~\ref{tab:bagOfFeatures}, none of the feature types alone yield higher F-scores than bag-of-words. On the other hand, when combined with BoW, all feature types (except the lexicalized POS-tags) perform better than BoW alone. However, none of them outperform BoW and BoL combined (F=$0.6278$, cf. Table~\ref{tab:ngrams}), or the combination of BoW+BoL with $n$-grams (F=$0.6656$).

@@

    \end{tabular}
  \end{center}
  \caption{Backoff from different combinations of $n$-grams. The models also
    contain bag-of-words, and BoF for each feature, as in Table \ref{tab:bagOfFeatures}. Each backoff combination is the one that achieved the best result.}
  \label{tab:ngrambackoff}
  \end{smaller}
\end{table}

Next, the $n$-grams and \emph{bag-of} features are combined with generalized versions of $n$-gram features using the `backoff' strategy described in the previous section. In Table~\ref{tab:ngrambackoff} we see that the lemma backoff consistently outperform the other feature types, but that even lemma backoff does not improve upon the results without backoff features. We test all possible backoff combinations.
% fixed fixme: forklar mer eksplisitt hvilke trekk som inngår i modellene i tabell 5, jeg klarte ikke gjøre rede for det selv.

@@

Lastly, we will test the addition of dependency triples to our models. We add
dependency triples consisting of word forms, both alone, and in conjunction
with feature backoffs. We test both head-backoff and modifier-backoff, and we report the variant that achieved the best results. As seen in Table
\ref{tab:depbackoff}, the inclusion of word form dependency triples improved
upon the simplest model, with an F-score of $0.6240$, compared to $0.6123$ for
bag-of-words alone. Dependency triples did not, however, improve upon the
results achieved by our previous best performer (F=$0.6656$). %, as the best model with dependency triples got an F-score of $0.6586$ compared to our best result of $0.6656$.
The addition of backoff also did not improve the results above the previous best performer.
%% Neither did the addition of backoff improve upon this. Adding POS backoff
%% to the `BoW+dep' configuration resulted in a slightly increased F-score of
%% $0.6298$. However, adding backoff to the `All' feature set only resulted in poorer F-scores, with the best feature backoff (also POS) resulting in an F-score of $0.6547$.

For the development data then, our best performer remains the feature set comprising bag-of-word forms, bag-of-lemmas, and word form bigrams and trigrams; with an F-score of $0.6656$. We will refer to this model as `lexical $n$-grams'. % fixed fixme: burde kanskje ha introdusert denne termen tidligere? Aksel: Jeg syns ikke det

@@

%% Before we perform our held-out testing, we will examine what types of errors we have in our model, when tested on the development set. 
The lexical $n$-gram feature set achieved a precision (P) of $0.7709$ and a recall (R) of $0.5857$. The performance of the same feature set improved slightly when using the SVM classifier (F=$0.6667$, P=$0.7629$, R=$0.5920$).
Compared with our initial BoW system, which had P=$0.6777$ and R=$0.5585$, we see that the majority of the improvement comes from the increase in precision. The increases in both models compared with BoW are statistically significant, with p-values of $1.3\mathrm{e}{-11}$ and $8.6\mathrm{e}{-11}$ for the lexical $n$-gram system using MaxEnt and SVM, respectively, using the Wilcoxon signed-rank test. When reviewing a random sub-sample of the false positives and false negatives, we see that the noisy data has caused some problems for the pre-processor. % fixme: kanskje forklare mer hva det siktes til her?
Another source of errors, specifically for precision, are comments which use multiple typically threatening words in a non-threatening context.

@@

We performed our final testing on the held-out test set using the basic BoW model and the lexical $n$-gram model, using both the MaxEnt and SVM classifiers. The held-out test set consists of 5,685 sentences, 281 of which are threats, and we train on the entire development set. As seen in Table~\ref{tab:heldout}, the $n$-gram models outperforms the BoW model by a good margin, with F-scores of $0.6885$ (SVM), $0.6860$ (MaxEnt), and $0.6562$ (BoW). However, the difference in F-scores between the two feature sets is not as large as on the development data, and they are in fact not statistically significant, with p-values of $0.14$ and $0.16$, when comparing the MaxEnt and SVM lexical n-gram models, respectively, to BoW, using Wilcoxon. At the same time, we see that all the models actually achieves higher scores on the held-out data than the development data, and this effect is particularly strong for the BoW model (with the F-score going up from $0.6123$ to $0.6562$). % fixme: noen teori om hvorfor vi ser denne effekten?
% fixed fixme: si noe som størrelsen på held-out dataene.
